---
title: "FinalProject"
output: html_document
date: "2023-03-07"
---
libraries
```{r}
library(dplyr)
library(tidyverse)
library(janitor)
```


Read the 9 years of data
```{r}
data2009 <- read.csv("/Users/kaiwhite/Documents/STOR 565/FinalProject/NFL QB SEASON BY SEASON STATS/pass-2009.csv")
data2010 <- read.csv("/Users/kaiwhite/Documents/STOR 565/FinalProject/NFL QB SEASON BY SEASON STATS/pass-2010.csv")
data2011 <- read.csv("/Users/kaiwhite/Documents/STOR 565/FinalProject/NFL QB SEASON BY SEASON STATS/pass-2011.csv")
data2012 <- read.csv("/Users/kaiwhite/Documents/STOR 565/FinalProject/NFL QB SEASON BY SEASON STATS/pass-2012.csv")
data2013 <- read.csv("/Users/kaiwhite/Documents/STOR 565/FinalProject/NFL QB SEASON BY SEASON STATS/pass-2013.csv")
data2014 <- read.csv("/Users/kaiwhite/Documents/STOR 565/FinalProject/NFL QB SEASON BY SEASON STATS/pass-2014.csv")
data2015 <- read.csv("/Users/kaiwhite/Documents/STOR 565/FinalProject/NFL QB SEASON BY SEASON STATS/pass-2015.csv")
data2016 <- read.csv("/Users/kaiwhite/Documents/STOR 565/FinalProject/NFL QB SEASON BY SEASON STATS/pass-2016.csv")
data2017 <- read.csv("/Users/kaiwhite/Documents/STOR 565/FinalProject/NFL QB SEASON BY SEASON STATS/pass-2017.csv")
data2018 <- read.csv("/Users/kaiwhite/Documents/STOR 565/FinalProject/NFL QB SEASON BY SEASON STATS/pass-2018.csv")

data2009$Tm <- sub("^", "2009", data2009$Tm)
data2010$Tm <- sub("^", "2010", data2010$Tm)
data2011$Tm <- sub("^", "2011", data2011$Tm)
data2012$Tm <- sub("^", "2012", data2012$Tm)
data2013$Tm <- sub("^", "2013", data2013$Tm)
data2014$Tm <- sub("^", "2014", data2014$Tm)
data2015$Tm <- sub("^", "2015", data2015$Tm)
data2016$Tm <- sub("^", "2016", data2016$Tm)
data2017$Tm <- sub("^", "2017", data2017$Tm)
data2018$Tm <- sub("^", "2018", data2018$Tm)
data2018$QBrec <- str_replace(data2018$QBrec, "/", "-")
data2018$QBrec <- str_replace(data2018$QBrec, "/", "-")
data2018$QBrec <- str_replace(data2018$QBrec, "2001", "1")
data2018$QBrec <- str_replace(data2018$QBrec, "2000", "0")
```

Combine the data into one large data set and split record. Remove any players with less than 34 pass attempts (average number of attempts for the bears in a game since 2013 who have thrown the least passes per game in the nfl)
```{r}
decadeData <- as.data.frame(bind_rows(data2009, data2010, data2011, data2012, data2013, data2014, data2015, data2016, data2017, data2018))
decadeData[c('Wins', 'Losses', 'Ties')] <- str_split_fixed(decadeData$QBrec, '-', 3)
decadeData <- subset(decadeData, select = -c(QBrec, Rk))
```

Need to Manage players with two teams in one season. Determine what to do with players who threw under X number of throws
```{r}

```

Question each teams success with another quarterback?
