---
title: "FinalProject"
output: html_document
date: "2023-03-07"
---
libraries
```{r}
library(dplyr)
library(tidyverse)
library(janitor)
library(leaps)
library(ISLR)
```


Read the 9 years of data
```{r}
data2009 <- read.csv("/Users/kaiwhite/Documents/STOR 565/FinalProject/NFL QB SEASON BY SEASON STATS/pass-2009.csv")
data2010 <- read.csv("/Users/kaiwhite/Documents/STOR 565/FinalProject/NFL QB SEASON BY SEASON STATS/pass-2010.csv")
data2011 <- read.csv("/Users/kaiwhite/Documents/STOR 565/FinalProject/NFL QB SEASON BY SEASON STATS/pass-2011.csv")
data2012 <- read.csv("/Users/kaiwhite/Documents/STOR 565/FinalProject/NFL QB SEASON BY SEASON STATS/pass-2012.csv")
data2013 <- read.csv("/Users/kaiwhite/Documents/STOR 565/FinalProject/NFL QB SEASON BY SEASON STATS/pass-2013.csv")
data2014 <- read.csv("/Users/kaiwhite/Documents/STOR 565/FinalProject/NFL QB SEASON BY SEASON STATS/pass-2014.csv")
data2015 <- read.csv("/Users/kaiwhite/Documents/STOR 565/FinalProject/NFL QB SEASON BY SEASON STATS/pass-2015.csv")
data2016 <- read.csv("/Users/kaiwhite/Documents/STOR 565/FinalProject/NFL QB SEASON BY SEASON STATS/pass-2016.csv")
data2017 <- read.csv("/Users/kaiwhite/Documents/STOR 565/FinalProject/NFL QB SEASON BY SEASON STATS/pass-2017.csv")
data2018 <- read.csv("/Users/kaiwhite/Documents/STOR 565/FinalProject/NFL QB SEASON BY SEASON STATS/pass-2018.csv")

data2009$Tm <- sub("^", "2009", data2009$Tm)
data2010$Tm <- sub("^", "2010", data2010$Tm)
data2011$Tm <- sub("^", "2011", data2011$Tm)
data2012$Tm <- sub("^", "2012", data2012$Tm)
data2013$Tm <- sub("^", "2013", data2013$Tm)
data2014$Tm <- sub("^", "2014", data2014$Tm)
data2015$Tm <- sub("^", "2015", data2015$Tm)
data2016$Tm <- sub("^", "2016", data2016$Tm)
data2017$Tm <- sub("^", "2017", data2017$Tm)
data2018$Tm <- sub("^", "2018", data2018$Tm)
data2018$QBrec <- str_replace(data2018$QBrec, "/", "-")
data2018$QBrec <- str_replace(data2018$QBrec, "/", "-")
data2018$QBrec <- str_replace(data2018$QBrec, "2001", "1")
data2018$QBrec <- str_replace(data2018$QBrec, "2000", "0")
```

Combine the data into one large data set and split record. Remove any players with less than 34 pass attempts (average number of attempts for the bears in a game since 2013 who have thrown the least passes per game in the nfl). Remove columns that are character or ties/losses/GWD to protect against overfitting. Removed Games started and Games played in order to not over value players that played every game
```{r}
decadeData <- as.data.frame(bind_rows(data2009, data2010, data2011, data2012, data2013, data2014, data2015, data2016, data2017, data2018))
decadeData[c('Wins', 'Losses', 'Ties')] <- str_split_fixed(decadeData$QBrec, '-', 3)
decadeData <- subset(decadeData, select = -c(QBrec, Rk, Player, Tm, Pos, Ties, Losses, GS, G, GWD))
```


Change type of wins, losses, ties to double and remove players with less than the league average of attempts per a game of 32 (subject to change) and remove players with N/A for record
```{r}
decadeData$Wins <- as.numeric(decadeData$Wins)
decadeData <- decadeData[decadeData$Att > 32, ] 
decadeData <- na.omit(decadeData)

df <- as.data.frame(decadeData)
```

correlation matrix
```{r}
pros.cor = cor(df)
#round(pros.cor,3)
```

split into test and train data.  find the test errors and plot them to find the number of variables related to the response and then obtain the coeffcients of the values
```{r}
set.seed(1)
train=sample(c(TRUE,FALSE), nrow(decadeData),rep=TRUE)
test=(!train)

regfit.best=regsubsets(Wins~.,data=decadeData[train,],nvmax=28)

test.mat=model.matrix(Wins~.,data=decadeData[test,])
testerror=rep(NA,23)
for(i in 1:22){
   coefi=coef(regfit.best,id=i)
   pred=test.mat[,names(coefi)]%*%coefi
   testerror[i]=mean((decadeData$Wins[test]-pred)^2)
}
testerror <- na.omit(testerror)
#testerror

x<- c(1:22)
plot(x,testerror, type="l")
points(which.min(testerror),testerror[which.min(testerror)], col="red",cex=2,pch=20)

coef(regfit.best,10)
```


apply k-fold cross validation
```{r}

```

Question each teams success with another quarterback?


First simple regression model. Find which variables are highly corrleated
```{r}
regression = lm(Wins ~ Age + Cmp + Att + ANY.A + TD + Int + QBR + X4QC + GWD, decadeData)
summary(regression)
```


